Variational Monte Carlo on Bosonic Systems

### 2018-04-05 project_1/article/article.tex
Add spellcheck to VMC intro

\section{Variational Monte Carlo}
    The variational principle states that for a given \emph{trial wavefunction},
    $\ket{\Psi_T}$, the expectation value of the Hamiltonian, $H$, will be an
    upper bound to the ground state energy, $E_0$ of the system.
    \begin{align}
        E_0 \leq E
        = \frac{\bra{\Psi_T}H\ket{\Psi_T}}{\bra{\Psi_T}\ket{\Psi_T}},
    \end{align}
    The complicated part of the variational principle is finding the minimum, or
    values close to the minimum. For a select few systems we can calculate this
    analytically, but for the interesting systems we quickly hit an intractable
    wall. To get around this we try to calculate the energy for a given
    Hamiltonian and a trial wavefunction for different variational parameters.
    The variance of the variational energy is given by
    \begin{align}
        \sigma^2
        &=
        \bra{\Psi_T}H^2\ket{\Psi_T}
        - \bra{\Psi_T}H\ket{\Psi_T}^2.
    \end{align}
    If we have found the ``true'' trial wavefunction $\ket{\Psi_T}$, i.e., the
    eigenfunction to the Hamiltonian $H$, we get $\sigma^2 = 0$. We are thus
    interested in trying to find the variational parameters in the trial
    wavefunction that minimizes the variance $\sigma^2$.

>>>>

\section{Variational Monte Carlo}
    The variational principle states that for a given \emph{trial wavefunction},
    $\ket{\Psi_T}$, the expectation value of the Hamiltonian, $H$, will be an
    upper bound to the ground state energy, $E_0$ of the system.
    \begin{align}
        E_0 \leq E
        = \frac{\bra{\Psi_T}H\ket{\Psi_T}}{\bra{\Psi_T}\ket{\Psi_T}},
    \end{align}
    The complicated part of the variational principle is finding the trial
    wavefunction that minimizes the energy. The strength in this method lies in
    introducing variational parameters in the trial wavefunction. Using these as
    degrees of freedom we can minimize the energy with respect to these in order
    to find an infimum to the ground state energy for the given trial
    wavefunction and Hamiltonian. For a select few systems we can calculate this
    analytically, but for the interesting systems we quickly hit an intractable
    wall as the systems become analytically unsolvable. To get around this we
    try to calculate the energy for a given Hamiltonian and a trial wavefunction
    for different variational parameters numerically.

    To determine if we have located a minimum we can use the variance of the
    variational energy.
    \begin{align}
        \sigma^2
        &=
        \frac{
            \bra{\Psi_T}H^2\ket{\Psi_T}
        }{
            \bra{\Psi_T}\ket{\Psi_T}
        }
        - \para{
            \frac{
                \bra{\Psi_T}H\ket{\Psi_T}
            }{
                \bra{\Psi_T}\ket{\Psi_T}
            }
        }^2.
    \end{align}
    If we have found the ``true'' trial wavefunction $\ket{\Psi_T}$ with the
    correct variational parameters, i.e., the eigenfunction to the Hamiltonian
    we get $\sigma^2 = 0$. We are thus interested in trying to find the
    variational parameters in the trial wavefunction that minimizes the
    variance.
